\chapwithtoc{Methods}
\label{methods}

Protein sequences and Pfam domain alignments were obtained from The European
Bioinformatics Institute's
FTP\footnote{\url{ftp://ftp.ebi.ac.uk/pub/databases/Pfam/releases/Pfam32.0/}}.
Archived files \texttt{Pfam-A.full} and \texttt{uniprot\_reference\_proteomes.dat}
corresponding to Pfam's release 32.0 were downloaded.
Protein family annotation software
pfamannot\footnote{\url{https://github.com/hamalcij/pfamannot}} has then been implemented
in C++17 to parse these files, and to extract architectures of all proteins containing at
least one \texttt{PF00069} domain, starting and ending positions of all domains present
within such proteins, primary sequence of the whole molecule, and organisms, from which
they originate.
Total 330,302 such proteins were identified, of which 127,697 were multi-domain proteins.

To reduce evolutionary noise, only human multi-domain protein kinases were selected for
further analysis.
The eukaryotic protein subcellular location predictor
DeepLoc-1.0~\cite{almagro2017deeploc} was applied to 542 human multi-domain protein
kinases with sequences spanning at most 6,000 residues due to DeepLoc's length limitation,
and molecules with their subcellular location predicted to cytoplasm or nucleus were
chosen, as the amino acid composition, thus also the physicochemical properties of
membrane proteins, differ significantly from their soluble
counterparts~\cite{capaldi1972low, von1988topogenic, tusnady1998principles}.
Besides, membrane proteins have their conformational degrees of freedom reduced due to
their placement in the lipid bilayer, and are therefore not suitable for the purpose of
this thesis.
Heterodimers were then elected from the emerging 244 cytosolic and nuclear human
multi-domain protein kinases, yielding the final dataset containing 117 molecules.

Two sets of physicochemical properties of the domain and inter-domain regions of the final
dataset were acquired.
The first set, which was in the spotlight of this study, consists of 8-mers composed of
the logarithm of linker's length, linker's iso-electric point, linker's percentage of
charged amino acids, linker's \emph{GRAVY index}~\cite{kyte1982simple}, kinase domain's
iso-electric point, kinase domain's GRAVY index, other domain's iso-electric point, and
other domain's GRAVY index.
These values were calculated with the ExPASy's ProtParam tool~\cite{gasteiger2005protein},
and their densities and correlation matrix across the whole dataset were computed.
In the second set, each linker is described with 553 physicochemical and
biochemical properties of amino acids from the AAindex database, version
9.2~\cite{nakai1988cluster, tomii1996analysis, kawashima1999aaindex, kawashima2000aaindex,
kawashima2007aaindex}.
Dimension reduction technique called \emph{UMAP}~\cite{mcinnes2018umap} was then applied
on various normalized subsets of both sets, thus producing clusters of proteins having
similar physicochemical attributes.

EC and GO terms present in the \texttt{uniprot\_reference\_proteomes.dat} file were
parsed.
The latter is a weakly hierarchical vocabulary~\cite{ashburner2000gene}, and the hierarchy
level of GO terms in the \texttt{uniprot\_reference\_proteomes.dat} file is not
standardized.
Therefore, for each protein, parents of its terms were recursively obtained from the
\texttt{go-basic.obo}
file\footnote{\url{http://current.geneontology.org/ontology/go-basic.obo}}, release
2020-06-01, thus enabling cluster analysis on different GO levels.
EC and GO terms were then embedded into the UMAP dimensionality reduction clustering, and
presence of unique terms within clusters was examined.
The same process was executed on density clusters as well.
Results were visualized using the Python 3.5.2 graphics package
Matplotlib~\cite{hunter2007matplotlib}, version 1.5.1.

% \chapter{Important first chapter}
% \label{chap:refs}
%
% First chapter usually builds the theoretical background necessary for readers to understand the rest of the thesis. You should summarize and reference a lot of existing literature and research.
%
% You should use the standard \emph{citations}\todo{Use \textbackslash{}emph command like this, to highlight the first occurrence of an important word or term. Reader will notice it, and hopefully remember the importance.}.
%
% \begin{description}
% \item[Obtaining bibTeX citation] Go to Google Scholar\footnote{\url{https://scholar.google.com}}\todo{This footnote is an acceptable way to `cite' webpages or URLs. Documents without proper titles, authors and publishers generally do not form citations. For this reason, avoid citations of wikipedia pages.}, find the relevant literature, click the tiny double-quote button below the link, and copy the bibTeX entry.
% \item[Saving the citation] Insert the bibTeX entry to the file \texttt{refs.bib}. On the first line of the entry you should see the short reference name --- from Scholar, it usually looks like \texttt{author2015title} --- you will use that to refer to the citation.
% \item[Using the citation] Use the \verb|\cite| command to typeset the citation number correctly in the text; a long citation description will be automaticaly added to the bibliography at the end of the thesis. Always use a non-breakable space before the citing parenthesis to avoid unacceptable line breaks:
% \begin{Verbatim}
% Trees utilize gravity to invade ye
% noble sires~\cite{newton1666apple}.
% \end{Verbatim}
% \item[Why should I bother with citations at all?] For two main reasons:
% \begin{itemize}
% \item You do not have to explain everything in the thesis; instead you send the reader to refer to details in some other literature. Use citations to simplify the detailed explanations.
% \item If you describe something that already exists without using a citation, the reviewer may think that you \emph{claim} to have invented it. Expectably, he will demand academic correctness, and, from your perspective, being accused of plagiarism is not a good starting point for a successful defense. Use citations to give the credit to people who invented what you build upon.
% \end{itemize}
% \item[How many citations should I use?]
% Cite any non-trivial building block or assumption that you use, if it is published in the literature. You do not have to cite trivia, such as the basic definitions taught in the introductory courses.
%
% The rule of thumb is that you should read, understand and briefly review at least around 4 scientific papers. A thesis that contains less than 3 sound citations will spark doubt in reviewers.
% \end{description}
%
% There are several main commands for inserting citations, used as follows:
% \begin{itemize}
% \item \citet{knuth1979tex} described a great system for typesetting theses.
% \item We are typesetting this thesis with LaTeX, which is based on TeX and Metafont~\cite{knuth1979tex}.
% \item TeX was expanded to LaTeX by \citet{lamport1994latex}, hence the name.
% \item Revered are the authors of these systems!~\cite{knuth1979tex,lamport1994latex}
% \end{itemize}
%
% \section{Some extra assorted hints before you start writing English}
%
% Strictly adhere to the English word order rules. The sentences follow a fixed structure with subject followed by a verb and an object (in this order). Exceptions to this rule must be handled specially, and usually separated by commas.
%
% Mind the rules for placing commas:
% \begin{itemize}
% \item Use the \emph{Oxford comma} before `and' and `or' at the end of a longer, comma-separated list of items. Certainly use it to disambiguate any possible mixtures of conjunctions: \textit{`The car is available in red, red and green, and green versions.'}
% \item Do not use the comma before subordinate clauses that begin with `that' (like this one). English does not use subordinate clauses as often as Slavic languages because the lack of a suitable word inflection method makes them hard to understand. In scientific English, try to avoid them as much as possible. Ask doubtfully whether each `which' and `when' is necessary --- most of these helper conjunctions can be removed by converting the clause to non-subordinate.
%
% As an usual example, \xxx{\textit{`The sentence, which I wrote, seemed ugly.'}} is perfectly bad; slightly improved by \xxx{\textit{`The sentence that I wrote seemed ugly.'}}, which can be easily reduced to \textit{`The sentence I wrote seemed ugly.'}. A final version with added storytelling value could say \textit{`I wrote a sentence but it seemed ugly.'}
% \item Consider placing extra commas around any parts of the sentence that break the usual word order, especially if they are longer than a single word.
% \end{itemize}
%
% Do not write long sentences. One sentence should contain exactly one fact. Multiple facts should be grouped in a paragraph to communicate one coherent idea. Paragraphs are grouped in labeled sections for a sole purpose of making the navigation in the thesis easier. Do not use the headings as `names for paragraphs' --- the text should make perfect sense even without all headings removed. If a section of your text contains one paragraph per heading, you might have wanted to write an explicit list instead.
%
% Every noun needs a determiner (`a', `the', `my', `some', \dots); the exceptions to this rule, such as non-adjectivized names and indeterminate plural, are relatively scarce. Without a determiner, a noun can be easily mistaken for something completely different, such as an adjective or a verb.
%
% Consult the books by \citet{glasman2010science} and \citet{sparling1989english} for more useful details.
